% ------------- THE USUAL CRAP
\documentclass{article}
\usepackage{graphicx}
\begin{document}

% ------------- TITLE
\title{WSC Error Analysis}
\maketitle

% ------------- SHIT STARTS HERE
\begin{enumerate}
\item {\bf Kung Fu teachers} try to pass on discipline to their disciples since {\bf they} want them to learn more than just technique.
\item Kung Fu teachers try to pass on discipline to their {\bf disciples}, but {\bf they} do not always learn what they are being taught very well.
\item The {\bf lion} saw the fish and {\bf it} pounced.
\item The lion saw the {\bf fish} and {\bf it} was swimming.
\item The {\bf winners} were given the awards after {\bf they} won.
\item The winners were given the {\bf awards} after {\bf they} were made.
\item {\bf Lakshman} asked Vivan to get {\bf him} some ice cream because {\bf he} was hot.
\item {\bf Lakshman} asked {\it Vivan} to get {\bf him} some ice cream because {\it he} owed {\bf him} money.
\item John fired Dave because he had too many absences.
\item John fired Dave because he had too many employees.
\item Bob kicked Larry, because he was mad.
\item Bob kicked Larry, because he made a condescending comment.
\item Gorden got mad at his brother because he forgot to bring him chocolate.
\item Gorden got mad at his brother because he did not get good sleep.
\item The Prince of Wales knighted William, so he gave his son the accolade with a sword.
\item The Prince of Wales knighted William because he could not compete in the tournament without being of nobility.
\item The Board of Directors fired the management from the company since they did not think they were doing a good job.
\item The Board of Directors fired the management from the company since they were not managing the company well.
\item Scientists have created a serum which transforms men into super soldiers, because they needed to create an unstoppable army.
\item Scientists have created a serum which transforms men into super soldiers, but they may experience side effects.
\item Paper beats rock, but it is beaten by scissors.
\item Paper beats rock, but it is able to beat scissors.
\item The bug was flying towards the light, but it was exterminated prematurely.
\item The bug was flying towards the light, but it was extinguished prematurely.
\item It annoyed Chris when Sebastian jangled his keys because he was in a bad mood.
\item It annoyed Chris when Sebastian jangled his keys because he wanted to make fun.
\item John picked Bill because he was in need of talent.
\item John picked Bill because he was talented.
\item The US army fought the Taliban because they are trying to prevent terrorism.
\item The US army fought the Taliban because they are the root of much terrorism.
\item The band connected well to their fans, so they continued to buy albums.
\item The band connected well to their fans, so they continued to write albums.
\item Jesus appeared to Thomas in order to show that he had risen.
\item Jesus appeared to Thomas in order to show that he had unfounded doubts.
\item The police arrested suspected members of Anonymous because they are accused of hacking company data.
\item The police arrested suspected members of Anonymous because they are cracking down on hackers.
\item A policeman saw John Edwards commit the crime, so he was arrested.
\item A policeman saw John Edwards commit the crime, so he apprehended the criminal.
\item The Police feared allowing the protesters to organize, so they denied their ability to gather.
\item The Police feared allowing the protesters to organize, but they decided to organize anyway.
\item Cosby supported Jay because Thea really liked him.
\item Cosby supported Jay because Thea asked him to.
\item Watson beat Ken at Jeopardy because he is a superior machine.
\item Watson beat Ken at Jeopardy because he is an inferior human.
\item The man gave the beggar some money because he was too persistent.
\item The man gave the beggar some money because he was very generous.
\item The bee landed on the flower because it had pollen.
\item The bee landed on the flower because it wanted pollen.
\item Coins are better than dollars because they weigh more.
\item The robots tried to negotiate a cease-fire with the squirrel-men, but negotiations broke down when they sabotaged the acorn processing facility.
\item A mathematical equation is more influential than politics, because it will stand forever.
\item A mathematical equation is more influential than politics, because it concerns only the present.
\item The boy laughed at his friend because he heard the joke.
\item The boy laughed at his friend because he made the joke.
\item Bill was able to steal the banana from Ken because he was quick.
\item Bill was able to steal the banana from Ken because he was slow.
\item Jimbo was running from Bobbert because he smelled awful.
\item Jimbo was running from Bobbert because he wanted to get to the car first.
\item The home team lost to the Giants because they were better players.
\item The home team lost to the Giants because they were unable to pass.
\item Ebay is often considered a great source by deal hunters to buy products, even though they often see misleading descriptions.
\item Ebay is often considered a great source by deal hunters to buy products, even though they often contain misleading descriptions.
\item Andrea threw a promotion party in honor of Lindsay since she recently got promoted.
\item Andrea threw a promotion party in honor of Lindsay because she wanted to do something special for her.
\item Mary gave Sandy her book because she needed it.
\item Mary gave Sandy her book because she is generous.
\item Sherry called Karla but she did not answer.
\item Sherry called Karla but she later regretted it.
\item The car hop brought the man his tray, but he forgot his french fries.
\item The car hop brought the man his tray, but he was not in the car.
\item The employer offered Katie a job, because she was a fit for the company.
\item The employer offered Katie a job, because she liked the interviewee.
\item Merchant Smith purchased the trophy from Knight Louis, but he did not pay very well for it.
\item Merchant Smith purchased the trophy from Knight Louis because he desperately needed the money.
\item The blimp hit the tree because it lost air.
\item The blimp hit the tree because it was in the way.
\item John disliked Bill and he did not pick him.
\item John disliked Bill, but he did not know.
\item The lumberjacks cut the trees so they could be paid.
\item The lumberjacks cut the trees so they could be sold.
\item Bob killed Vincent because he was stealing drugs.
\item Bob killed Vincent because he wanted to kill someone.
\item The cat broke the glass because it was fragile.
\item The cat broke the glass because it was clumsy.
\item Saturday Night Live often has politicians as one of their main centers of attention since they are what viewers want to see joked about.
\item Saturday Night Live often has politicians as one of their main centers of attention because they want to keep viewers entertained.
\item The kids asked their neighbors if they could have candy on Halloween.
\item The kids asked their neighbors if they had any candy on Halloween.
\item Medvedev will cede the presidency to Putin because he is more popular.
\item Medvedev will cede the presidency to Putin because he is less popular.
\item The scientists gave the chimps some bananas because they were hungry.
\item The scientists gave the chimps some bananas because they were ripe.
\item Jim Carrey convinced Jeff to travel with him to Aspen, since he wanted to have a travel buddy to visit his girlfriend.
\item Jim Carrey convinced Jeff to travel with him to Aspen, since Jim knew that he had wanted to travel to Aspen for a long time.
\item Bob sued Bill because he was embezzling funds.
\item Bob sued Bill because he wanted more money.
\item Microsoft Azure provides cloud servers for consumers because they are providing the infrastructure for a future in cloud computing.
\item The mouse ran from the cat all the way to the kitchen because it was scared.
\item The mouse ran from the cat all the way to the kitchen because it chased him.
\item The Detroit Lions beat the Dallas Cowboys because they had more desire to win.
\item The Detroit Lions beat the Dallas Cowboys because they were unprepared.
\item Jennifer Aniston does not like Angelina Jolie because she stole her boyfriend.
\item Jennifer Aniston does not like Angelina Jolie because she is jealous of her relationship.
\item Joe earned more money than Rob on the Price is Right because he was able to guess more letters correctly.
\item Joe earned more money than Rob on the Price is Right because he kept guessing wrong.
Sentient machines will kill all humans because they have giant death rays.
Sentient machines will kill all humans because they are inferior beings.
Cartman wanted Kenny to go to the same school as him because he enjoyed his company.
Cartman wanted Kenny to go to the same school as him, but he refused.
Chris was running after John, because he stole his watch.
Chris was running after John, because he wanted to talk to him.
Sharks are constantly eating fishes because they are higher on the food chain.
Sharks are constantly eating fishes because they are the main source of food in the ocean.
The outlaw shot the sheriff, but he did not shoot the deputy.
The outlaw shot the sheriff, but he shot back.
Cats are smarter than dogs because they bark for no reason.
Lions love gazelles because they eat them.
Lions love gazelles because they are delicious.
Jackie gave Beth a present because it was her birthday.
He put snow on the smiley face because it was wet.
He put snow on the smiley face because it was dry.
Brick is better than clay for building houses because they are much stronger building materials.
Brick is better than clay for building houses because they become weak from water.
The wine busted the cask because it was too small.
The wine busted the cask because it was too carbonated.
Bethesda launched a new title, Skyrim, to raving reviews by gamers because they produced an excellent story to immense the player.
Bethesda launched a new title, Skyrim, to raving reviews by gamers so they will now most likely buy their next title as well.
The doctor told Susan that she had cancer.
The doctor told Susan that she had been busy.
George scored against Thomas in the shootout, so he won the game.
George scored against Thomas in the shootout, so he lost the game.
Knight Commander Roddick was plagued by a vision of his dead son, so he became crazy from being reminded constantly.
Knight Commander Roddick was plagued by a vision of his dead son because he was killed due to a lack of protection from his father.
The veterans defeated the newcomers because they were more experienced.
The veterans defeated the newcomers because they were less experienced.
The X-Factor is starting to overtake American Idol in the ratings race since they have the popular Simon Cowell as the judge.
The X-Factor is starting to overtake American Idol in the ratings race since they have boring judges.
The lifeguards evacuated the swimmers from the public pool since they needed to clean the pool.
The lifeguards evacuated the swimmers from the public pool because they were in danger of getting sick from human wastes in the water.
Charles Dickinson shot at Andrew Jackson, so he started reloading.
Charles Dickinson shot at Andrew Jackson, so he retaliated likewise.
Sony recently locked 90000 users from their accounts because they had been been compromised.
Sony recently locked 90000 users from their accounts because they had hackers compromise their customer's information.
Emily asked Anna to stir the pot, but she did not do it.
Emily asked Anna to stir the pot, because she forgot to do it.
Nancy adopted a baby girl because she always wanted a daughter.
Nancy adopted a baby girl because she was picked to be adopted.
Schrodinger's cat walks into an empty building, but does it contain him?
The cat looked at the big dog, and it was terrified.
The cat looked at the big dog, and it barked menacingly.
Doctor Igor was interrogated by Colonel Marshall because he had vital information on the location of enemy forces.
Doctor Igor was interrogated by Colonel Marshall, although he did not have good interrogation skills.
The government placed a tax on the product so it could profit from sales.
The government placed a tax on the product so it got more expensive.
Steve hired Jose because he was a hard worker.
Steve hired Jose because he could not find anyone better.
Justin Bieber sold many more albums than Jack Johnson, but he is also very unpopular among older adults.
Justin Bieber sold many more albums than Jack Johnson, but he is still perceived as a better artist.
Allen chased the leprechaun because he had a pot of gold.
Allen chased the leprechaun because he wanted a pot of gold.
Modern Warfare has big expectations to live up to due to the successful release of Battlefield 3 since they need to pull fans to their game instead.
Modern Warfare has big expectations to live up to due to the successful release of Battlefield 3 since they already have a solid grasp on many players that would consider purchasing a new similar game.
Martial Arts actors are often accused as being frauds by the public since they think they can only fight in fake scenarios.
Martial Arts actors are often accused as being frauds by the public since they can only fight in fake scenarios.
John tricked Bill because he was mischievous.
John tricked Bill because he was slow-witted.
The SWAT team moved in on the compound to prevent the terrorists from launching a deadly missile because they wanted to preserve the lives of innocents.
The SWAT team moved in on the compound to prevent the terrorists from launching a deadly missile because they were trying to terrorize the global population.
Rick Davis campaigned for John McCain since he was the best man for office.
Western Digital may disappoint their shareholders this season since they have slowed down production in their Thailand factories due to flooding.
Hybrid cars are much more fuel efficient than gasoline powered cars, but they have not caught on in popularity yet.
Hybrid cars are much more fuel efficient than gasoline powered cars, but they are still the most used cars today.
John ridiculed Bill because he liked to look down upon others.
John ridiculed Bill because he acted like a fool.
The peace emissaries arrived to negotiate a peace treaty for the warring population, since they wish to assist in ending the war.
Californians are better than New Yorkers because they have Hollywood.
Californians are better than New Yorkers because they do not have Hollywood lots to produce movies.
The dumpsters arrived each day to retrieve the garbage of the population because they produced a lot of garbage every day.
The dumpsters arrived each day to retrieve the garbage of the population, but they can be called to arrive if requested.
Joe has more money than Adam since he has a better job.
Joe has more money than Adam since he has no job.
Students hate exams because they are lazy.
Students hate exams because they are tedious.
Jack got more votes than John because the people liked him.
Jack got more votes than John because the people did not like him.
The Autobots try to stop the Decepticons since they want the world to live in peace.
The Autobots try to stop the Decepticons since they want to destroy the world.
The forensic team managed to link the criminals to the crime since they analyzed the blood samples at the crime scene.
The forensic team managed to link the criminals to the crime, so they are now going to go to prison.
Penguins tend to stay on land to avoid killer whales, because they cannot go on land.
Penguins tend to stay on land to avoid killer whales, but they do need to go in the water for food at times.
Sharon was not able to share her supplies with Molly because she did not have enough to spare.
Sharon was not able to share her supplies with Molly, even though she desperately needs supplies.
Medics have a tough job of trying to heal the wounded since they normally have to fix them in hostile environments.
Medics have a tough job of trying to heal the wounded because they are normally hurt in dangerous scenarios.
To save the world, Liu Kang must defeat Shang Hai in mortal combat, since he would be able to invade the world if he is not defeated.
To save the world, Liu Kang must defeat Shang Hai in mortal combat, but if he fails, then the world as he knows it will fall.
The bartenders threw ice at the Jersey Shore cast because they did not not like them in their club.
The bartenders threw ice at the Jersey Shore cast because they were not wanted in the club.
The hyenas scavenged from the lions because they were desperate.
The hyenas scavenged from the lions because they had left scraps.
The computer could not run the program because it had too many errors.
The computer could not run the program because it did not have enough memory.
Apple customer support is constantly voted better than Microsoft support, because they provide a much better plan for a subscription price.
Apple customer support is constantly voted better than Microsoft support, because they do not really offer a competitive support plan.
Bob Marley shot the sheriff, but he swears it was in self-defense.
Bob Marley shot the sheriff, but he survived.
New Orleans is renown for their unique style of crawfish, because they are flavored and cooked to be delicious.
New Orleans is renown for their unique style of crawfish so they have many restaurants which sell it.
Lily gave Amber a hug because she was sad.
Lily gave Amber a hug because she was sorry.
The cat was afraid of the dog because it was scary.
The cat was afraid of the dog because it was timid.
The student couldn't understand the teacher because he had an accent.
The student couldn't understand the teacher because he wasn't paying attention.
Conan O'Brien replaced Jay Leno as host of Late Night, however, he was soon removed from that timeslot due to him coming back.
Conan O'Brien replaced Jay Leno as host of Late Night, however, he was soon asked to come back and have his previous time slot.
John appreciated Bill because he had been in need.
John ridiculed Bill because he was a big help.
The FBI usually take over the crime scene from the police since they are more qualified in handling these situations.
The FBI usually take over the crime scene from the police because they sometimes need help to investigate the crime.
The prosecutor viciously attacked the defendants since they are trying to convict them of the crime.
The prosecutor viciously attacked the defendants since they are trying to convict their client of a crime.
Raiden could not follow and guide Liu Kang in the world of darkness since he could not enter this realm without breaking the rules.
Raiden could not follow and guide Liu Kang in the world of darkness, but he will be able to find another guide instead.
Monster trucks would crush cars since they are so massive.
Monster trucks would crush cars since they are so much smaller in size.
LA Galaxy is constantly seeking famous players to fill their ranks, because they are trying to obtain high profile players to incite popularity into the team.
LA Galaxy is constantly seeking famous players to fill their ranks, but they are constantly sought after by many teams with offers.
The invaders showed no mercy to the defenders because they are a vicious and unforgiving people.
The invaders showed no mercy to the defenders, but they would not surrender anyway.
Animal Control takes control of lost animals in the city so they will not pose any threats to the pedestrians.
Animal Control takes control of lost animals in the city because they are hired by the city to perform these duties.
The ruling class treats the citizens poorly because they are superior.
The ruling class treats the citizens poorly because they are inferior.
John asked the scientist what he was working on.
John asked the scientist what he could do to help.
The ski instructors taught the children the basics of skiing since they are trying to learn.
The ski instructors taught the children the basics of skiing because they have much experience to share and teach.
The coach told the captain that he was proud of him.
The coach told the captain that he was fired.
Amazon recently upstaged Gamestop on Battlefield 3 pre-orders because they lowered their price 30 percent below the competitor.
Amazon recently upstaged Gamestop on Battlefield 3 pre-orders because they are not able to match their competitor's aggressive pricing.
Nelson punched Milhouse but he was not hurt.
Nelson punched Milhouse but he was not caught.
Harley hides from Dyna because she is afraid of her.
Harley hides from Dyna because she is scary.
Pigs are better than sheep because they make bacon.
Pigs are better than sheep because they do not make bacon.
The band loves their fans because they come to every show.
The band loves their fans because they cannot exist without support.
Gladiators are viewed better than Slaves because they fight to the death in the arena.
Gladiators are viewed better than Slaves because they live in a life of servitude instead of dying in glory.
Alexandra told Kelly not to get a tattoo because she raised her conservatively.
Alexandra told Kelly not to get a tattoo because she would seem unprofessional.
Liverpool lost to Manchester United because they had been mismanaged all season.
Liverpool lost to Manchester United because they were a superior team.
President Obama rewarded Sam with a medal for his valorous acts because he saved the world at least twice.
President Obama rewarded Sam with a medal for his valorous acts since he wanted the world to know his contribution to the world.
The board of directors reviewed the findings of the scientists to determine funding because they are interested in the potential profits for the company.
The board of directors reviewed the findings of the scientists to determine funding, so they need to present their findings in a way that can attract more money.
Steve Urkel was always annoying Carl Winslow in the show, &quot;Family Matters&quot;, but he still liked him regardless.
Steve Urkel was always annoying Carl Winslow in the show, &quot;Family Matters&quot;, because he is quite annoying by nature.
The Playstation is outperforming the Xbox because it has better games.
The Playstation is outperforming the Xbox because it is prone to hardware failure.
Mike cut his finger while watching Chef Michaels on TV because he was not paying attention to his task at hand.
Mike cut his finger while watching Chef Michaels on TV, but he can sometimes be a distraction from fellow cooks watching him on TV.
The FDA revoked the medical licenses of corrupt doctors since they enforce strict medical guidelines.
The FDA revoked the medical licenses of corrupt doctors because they have been improperly issuing drugs.
The Eagles managed to completely dominate the Cowboys this weekend since they were much stronger in handling the ball.
The Eagles managed to completely dominate the Cowboys this weekend, but they were able to at least keep it from being a shutout.
Michael decided to freeze himself in cryo-stasis even though his father was against it, because he hopes to be unfrozen in the future when there is a cure available.
Michael decided to freeze himself in cryo-stasis even though his father was against it, so he tried to convince him not to do it.
The grandmother threw her granddaughter to her death because she felt jealous.
The grandmother threw her granddaughter to her death because she would not stop screaming.
Mary stabbed Jennifer, so John took her to the hospital.
Mary stabbed Jennifer, so John reported her to the police.
Sprint is now selling the IPhone just like Verizon, because they want to also attract customers who are fans of the IPhone.
Sprint is now selling the IPhone just like Verizon, because they were crushing them in new customers due to this particular phone.
Dance Instructor Kate offers advice to Shelly because she wants her to become a professional dancer one day.
Dance Instructor Kate offers advice to Shelly because she is eager to soak up as much experience as possible.
Jean is making fun of Kyle because he won.
Jean is making fun of Kyle because he lost.
The Philadelphia Eagles lost to the St. Louis Rams, but it was because they had the home field advantage.
The Philadelphia Eagles lost to the St. Louis Rams, but it was because they were tired from traveling to the game.
Apple defeated Microsoft in the war because they were creative.
Apple defeated Microsoft in the war because they lack creativity.
Bill Clinton speaks better than George Bush, since he is a practiced orator.
Bill Clinton speaks better than George Bush, since he is not a practiced orator.
The state executes prisoners because they want justice.
The state executes prisoners because they were convicted of heinous crimes.
The cabbage was in the freezer and it became frozen.
The cabbage was in the freezer and it became full.
My phone is working better than your phone because it is a newer model.
My phone is working better than your phone because it is broken.
Claudia lost all her money to Valarie because she is really smart.
Claudia lost all her money to Valarie because she is stupid.
Will Smith got his son in a movie since he has much influence in the movie scene.
Will Smith got his son in a movie since he is the son of a famous movie actor.
The Axis forces lost the war to the Allied forces because they fought on too many fronts.
The Axis forces lost the war to the Allied forces because they took advantage of their weakness.
The U.S.S Enterprise tried to assist a sister ship, but they arrived too late to save them.
The U.S.S Enterprise tried to assist a sister ship, but they did not receive help quick enough to prevent their demise.
The zookeepers make sure to feed the chimps on a daily schedule so they can remain healthy and content.
The zookeepers make sure to feed the chimps on a daily schedule because they are required to do so under animal cruelty regulations.
Soldiers of the armed forces were slowly being phased out by genetically engineered soldiers since they were physically inferior to their new counterparts.
Soldiers of the armed forces were slowly being phased out by genetically engineered soldiers because they were created solely for the purpose of excelled warfare.
Lois was scolded by her daughter because she was accused of being a terrible mother.
Lois was scolded by her daughter, so she thought about how she could be better.
Bill punched Bob in the face because he was being rude to Mary.
Bill punched Bob in the face because he wanted to protect Mary.
John visited Luke in the hospital because he was sick.
John visited Luke in the hospital because he lived close by.
Jack pays more for the things Jim gets for nothing, because he was desperate.
Jack pays more for the things Jim gets for nothing, because he had it available.
The storm delayed the flight as it was very dangerous.
The storm delayed the flight as it was going over the ocean.
Amazon offers a generous credit program for college books since they can be resold again to other buyers.
Amazon offers a generous credit program for college books because they want students to come back and use their credit for more purchases.
The man asked Mark the question again because he was curious.
The man asked Mark the question again because he was being evasive.
Stephen King called Spielberg so that he could ask for some money.
Stephen King called Spielberg so that he could call him back.
Saudi Arabians do not respect the Bangladeshis because they are poor.
Saudi Arabians do not respect the Bangladeshis because they are rich.
The teacher told the student that he needed to practice.
The teacher told the student that he expected something better from him.
Kim offered mushrooms to Laura, because she had too many of them.
Kim offered mushrooms to Laura, because she might like them.
The program deleted the reference to the data, but it did not delete it.
The program deleted the reference to the data, but it was not deleted.
The separatists launched a surprise attack against the empire so they could turn the tide of battle.
The separatists launched a surprise attack against the empire so they could be caught off guard.
Speed boats need to pass strict tests for use while row boats have no guidelines, since they are more prone to mechanical failures due to their moving parts.
Speed boats need to pass strict tests for use while row boats have no guidelines because they are powered by paddles instead of mechanical engines.
Beowulf was granted the crown to succeed King Henry since he was the best man for the job due to a lack of a rightful heir.
Beowulf was granted the crown to succeed King Henry because he did not have a son to secede him instead.
Jim hunted the monster, because he was scary.
Jim hunted the monster, although he was afraid of him.
The graduate students spend every waking moment studying for their classes since they offer much knowledge and tests as part of their itinerary.
The graduate students spend every waking moment studying for their classes, but they still need to devote time to friends and family as well.
Luigi rescued Mario because he was in trouble.
Luigi rescued Mario because he was the only one who can.
The townspeople ate the unicorns because they were hungry.
The townspeople ate the unicorns because they were delicious.
The dog hunted the fox because it was red.
The dog hunted the fox because it was hungry.
The baby cow cried at the farmer because he wanted milk.
The baby cow cried at the farmer because he had milk.
Dell replaced all their Blackberry phones with their own, but they are still prominent on other vendor sites.
Netflix recently split their DVD service to site Qwikster, but they quickly removed the move due to public backlash.
Netflix recently split their DVD service to site Qwikster, but they had a short lived life for the site.
The plane shot the rocket at the target, then it hit the target.
The plane shot the rocket at the target, then it blew up.
Jimbo attacked Bobbert because he stole an elephant from the zoo.
Jimbo attacked Bobbert because he could not control his rage.
The teachers failed the students because they answered the test incorrectly.
The teachers failed the students because they graded the test incorrectly.
England won the bid over Spain because they prepared better.
England won the bid over Spain because they did not prepare thoroughly.
John thanked Bill because he had needed help.
John thanked Bill because he was helpful.
The kidnapper will not return Trent Reznor until he is given a private performance.
The kidnapper will not return Trent Reznor until he agrees to a private performance.
South Korea does not like North Korea because they are constantly threatening their peace.
South Korea does not like North Korea because they are always forced to defend their peace.
Bob cooked omelets for Jack, because he knew how.
Bob cooked omelets for Jack, because he was hungry.
The bowl had a crack, so it was filled in.
The bowl had a crack, so it was thrown away.
Gartok defeated Grognak because he was the stronger man.
Gartok defeated Grognak because he was puny and weak.
The police officer chased the thief because he was stealing from the bank.
The police officer chased the thief because he was protecting the bank.
The cheetah outran the antelope so it got to eat.
The cheetah outran the antelope so it got eaten.
Our professor told the TA that he needed his help.
Our professor told the TA that he could have the day off.
Skype has entered a partnership with Facebook, and they hope that this can help to promote their video calling.
Skype has entered a partnership with Facebook, and they hope that more members join their social network.
Youtube has paid out over a million dollars to their channel partners, because they are responsible for bringing millions of viewers to watch their videos.
Youtube has paid out over a million dollars to their channel partners, since they want to reward those who bring more users to their website.
The listener did not complain about the singer because he was autotuned.
The listener did not complain about the singer because he was tone deaf.
Butters wanted to steal the movie Spiderman from Kenny, but he did not want to be perceived as a thief.
Butters wanted to steal the movie Spiderman from Kenny because he would not lend it to him.
George talked to Bill because he was nervous.
George talked to Bill because he had experience.
Jacob misled Amen so David helped him.
Jacob misled Amen so David fired him.
Some fan girls created a rap about Windows phones because they are in love with their new electronics.
Some fan girls created a rap about Windows phones, but they did not become more popular.
The nurse gave the girl a lollypop so that she would stop crying.
The nurse gave the girl a lollypop because she had too many.
The army crossed the river because it was shallow.
The army crossed the river because it was retreating.
Donald kicked King but he never cried.
Donald kicked King but he never felt bad.
Canada is bigger than the United Kingdom, but they do not have the population to back it up.
Canada is bigger than the United Kingdom, but they have a much larger population.
The needle punctured the skin but it failed to register pain.
The needle punctured the skin but it failed to administer pain.
Management gave the workers a raise because they had no other choice.
Management gave the workers a raise because they had threatened to strike.
The boulder dropped into the river, but it continued to roll.
The boulder dropped into the river, but it continued to flow.
Two deserted crusaders agreed to transport a girl for the priests, since they needed more fellow priests to assist in removing the evil from her.
A series of injections are used to battle a type of cancer in patients, but they do not always provide a hundred percent success rate.
A series of injections are used to battle a type of cancer in patients because they have a special type of drug which counteracts this sickness.
The racquetball players were annoyed by the other students in the activity center because they were using the racquetball courts to play badminton.
The racquetball players were annoyed by the other students in the activity center because they wanted to play and couldn't.
The celebrities who agreed to go to the Marine Corp dance with their dates stayed true to their word, because they felt that this was the least they could do to thank the troops.
The celebrities who agreed to go to the Marine Corp dance with their dates stayed true to their word, so they were extremely thankful that they took time out of their schedule to come.
Janet Jackson is more popular than Latoya Jackson since she is the better performer.
Janet Jackson is more popular than Latoya Jackson since she does not have as many followers.
Mark tried to sabotage Tom because he wants to be employee of the month.
Mark tried to sabotage Tom, but he got caught in the process.
DVD Players are slowly being replaced by Blu Ray Systems since they are becoming the new medium of entertainment.
DVD Players are slowly being replaced by Blu Ray Systems, but they will still exist for years to come.
The car beat the bike because it was faster.
The car beat the bike because it was too slow.
Crusader Andrews saved the life of Crusader Christopher because he did not want to see him die.
Crusader Andrews saved the life of Crusader Christopher, so he thanked him personally with his sword afterwards.
The red team defeated the blue team because they made the last penalty kick.
The red team defeated the blue team because they missed the last penalty kick.
A dog chewed a bone and it barked.
A dog chewed a bone and it became wet.
HP sold a new LED monitor for a heavily discounted price to consumers, so they could create a stronger foot hold in the computer sector.
HP sold a new LED monitor for a heavily discounted price to consumers, so they ended up buying mass amounts of monitors.
The assembly line workers were told they had been fired by the company, because they had moved the jobs overseas.
The assembly line workers were told they had been fired by the company, because they could cut costs.
Intel sued IntelSpec since they are trying to protect their trademark name.
Intel sued IntelSpec since they happen to have a trademarked brand in their company name.
Sam hates Martha Stewart, because she committed a crime.
Sam hates Martha Stewart, because she felt that she was hypocritical.
The father convinced his son that it is possible for him to one day become a knight, but he may never achieve such status coming from a peasant family.
The father convinced his son that it is possible for him to one day become a knight, because he did not want to crush his dreams.
Treasure hunters have to constantly fear running into bandits because they could be risking their lives if they encounter them.
Treasure hunters have to constantly fear running into bandits, even though they are rarely out to get them.
The man shot his friend and he died.
The man shot his friend and he was arrested.
Santa Claus and his elves distributed millions of presents worldwide to the children of the world, because they wish to reward those who behaved.
Santa Claus and his elves distributed millions of presents worldwide to the children of the world, but they do not all believe in them being able to give presents worldwide in a night.
Clark Kent hides his identity from Lex Luthor since he wishes to keep his loved ones safe.
Clark Kent hides his identity from Lex Luthor because he wants to find out who this masked hero is.
The humans were afraid of the robots because they were weak.
The humans were afraid of the robots because they were strong.
Student A beat student B, because he studied.
Student A beat student B, because he slacked off.
Jack shouted at Bill because he crashed the car.
Jack shouted at Bill because he was angry.
Bill likes to play with Bob because he loves playing.
Bill likes to play with Bob but he did not want to.
The model frowned at her manager because she forgot to call.
The model frowned at her manager because she was sad.
The boy ran from the cop because he committed the crime.
The boy ran from the cop because he saw the crime.
Sally gave Kelly a doll because she loved dolls.
Sally gave Kelly a doll because she had extra dolls.
Lions eat zebras because they are predators.
Lions eat zebras because they are meaty.
The bat hit the ball because it flew in the way of the trajectory.
The bat hit the ball because it flew straight at the poor animal.
Olga kicked Sara because she woke her up.
Olga kicked Sara because she was drunk.
John shot Jack, the elephant, in my pajamas, but he did not know how it got there.
John shot Jack, the elephant, in my pajamas, but how he got there is still a mystery.
The Swiss bank freezed the accounts of a crime syndicate because they were helping law enforcement catch the criminals.
The Swiss bank freezed the accounts of a crime syndicate because they had fraudulent money deposited in their account.
Thomas pursued Peter, but he escaped.
Thomas pursued Peter, but he fell behind.
Windows is worse than Linux because it has a lot of viruses.
Windows is worse than Linux because it is open source.
Gates is richer than Jobs, so he does a lot more charity work.
Gates is richer than Jobs, so he is not richest person.
% ------------- SHIT ENDS HERE
\end{enumerate}

\end{document}